Networked Character Devices

### 2011-12-08 report/presentation.tex
presentation: high level arch
presentation: server medium level

  Our system uses a basic client server model
\end{frame}

>>>>

  \begin{itemize}
    \item<1-> Our system uses a basic client server model
    \item<2-> The client initiates all exchanges, the server replies
  \end{itemize}
\end{frame}

\begin{frame}[c]{High Level}
  \includegraphics[width=0.8\textwidth]{arch-02.png}

  \begin{itemize}
    \item<1-> The server side resides entirely in a single kernel module
    \item<2-> The client side is a standard userspace server
  \end{itemize}
\end{frame}

\begin{frame}[c]{Server Medium Level}
  \includegraphics[width=0.4\textwidth]{arch-03.png}

  \begin{itemize}
    \item<1-> By default, devices are exposed under /dev/netchar
    \item<2-> In the future, we should be able to choose any name
  \end{itemize}
\end{frame}
